Portfolio conservation of exploited metapopulations\\Portfolio prioritization of salmon conservation\\Portfolio prioritization of metapopulation conservation\\Prioritizing metapopulation conservation through the lens of portfolio theory

### 2013-06-06 inst/ms/ms.tex
A variety of ms updates; especially adding outlines

\begin{itemize}
\item
  Portfolio optimization reveals\ldots{}
\item
  something more general with animals instead of just salmon?
\item
  Portfolio theory reveals conservation strategies that\ldots{}
\item
  Intelligent tinkering with ecological portfolios: patterns of
  environmental response diversity drive salmon conservation priorities
\item
  Keeping every cog and wheel\ldots{}
\end{itemize}

\section{Abstract}

@@

Managing risk is fundamental to the conservation of an endangered
species. When an endangered species exists as a metapopulation, we can
manage risk at two levels: at the population level or at the
metapopulation level. Typically we treat sources of risk at the
metapopulation level as external and uncontrollable and so we manage
risk by altering fishing or hunting on a population level as well as
improving the connectivity of populations.

The management of financial portfolios provides another way of
considering risk. Economists consider the risk and performance of a
financial portfolio as a function of the weighting of individual assets
that make up the portfolio. Modern Portfolio Theory (MPT) proposes that
there is a set of portfolios that maximizes expected return for a level
of expected risk or minimizes expected risk for a level of expected
return \citep{markowitz1952, markowitz1959}. This optimal set contains
portfolios that range along a continuum of risk-tolerance; economists
refer to this set as the efficient frontier.

Portfolios provide another way of managing risk - explain mean-variance
optimization and how this translates to ecology
\citep{figge2004}\citep{hoekstra2012}
\citep[\citet{ando2012}]{ando2011}\citep[\citet{markowitz1959}]{markowitz1952}

We use salmon as an example, describe the components of the example,
provide references on metapopulation existence \citep{schindler2010}

Research questions, and briefly our approach - Monte Carlo simulation
modelling, as simple a model as possible while retaining important
realistic aspects of salmon metapopulations

Here, we ask how a portfolio approach to managing risk can inform the
spatial conservation of metapopulations in a changing world. To answer
this, we develop a salmon metapopulation simulation in which
population-specific productivity is driven by spatially-distributed
environmental tolerance and patterns of short- and long-term
environmental change. We then implement different conservation ``rules
of thumb'' that control the population-specific carrying capacities and
evaluate the salmon portfolios along risk and return axes, similarly to
how financial portfolios are assessed. We show\ldots{} (briefly)

@@

We developed a salmon metapopulation simulation model that includes a
stock-recruit relationship, demographic stochasticity, straying between
populations, varying responses to the environment, escapement target
setting, and implementation uncertainty. Under two kinds of
environmental regimes we tested different conservation rules of thumb
and evaluated these plans in risk-return space similar to how financial
managers evaluate financial portfolios. See Figure \ref{f:sim-flow} for
an illustration of the overall simulation structure. We provide a
package \texttt{metafolio} for the statistical software \texttt{R}
\citep{r2013} as an appendix, which can be used to carry out the
simulations and analyses we describe in this paper.

@@

In our ecological portfolios, we defined assets as stream-level
populations and the portfolios as salmon metapopulations (Table
\ref{t:port}). We use the terms \textit{stream} and \textit{populations}
interchangeably to represent the portfolio assets. The portfolio
investors were the stakeholders in the fishery and metapopulation
performance. For example, we could consider fisheries managers,
conservation agencies, or First Nations groups as investors. We defined
asset value as the abundance of returning salmon in each stream and
value of the portfolio as the overall metapopulation abundance. In this
scenario, the equivalent to financial rate of return is the
generation-to-generation rate of change of metapopulation abundance. We
defined the financial asset investment weights as the carrying capacity
of the stream populations --- specifically the unfinished equilibrium
stock size --- since maintaining or restoring habitat requires money,
time, and resources.

@@

The salmon metapopulation dynamics in our simulation were governed by a
spawner-return relationship with stochastic noise and by straying
between populations.

@@

We manipulated the capacity and productivity parameters $b$ and $a$ as
part of the portfolio simulation. The capacity parameters $b_i$ were
controlled by the investment weights in the populations. For example, a
large investment in a stream was represented by a larger unfished
equilibrium stock size $b$ for stream $i$. The productivity parameters
$a_{ti}$ were controlled by the interaction between an environmental
signal and the stream-level population environmental tolerance curves.
The environmental tolerance curves were generated as parabolas according
to

@@

\noindent where $W_i$ controls the width of the curve for population
$i$, $e_t$ represents the environmental value at generation $t$,
$e_i^{\mathrm{opt}}$ represents the optimal environmental value for
population $i$, and $a_i^{\mathrm{max}}$ represents the maximum possible
$a$ value for population $i$. See Figure \ref{f:all-curves} for example
environmental tolerance curves.

@@

Our simulation used a simple set of rules to establish escapement
targets and harvest the fish. Every $f_\mathrm{assess}$ years (base case
of five years) our simulation fitted a spawner-return function and
target harvest rate $H_{\mathrm{tar}}$ was set based on
\citet{hilborn1992} as

@@

\noindent Further, to establish a range of spawner-return values and to
mimic the start of an open-access fishery, for the first 20 (TODO
variable) years we drew the fraction of fish harvested randomly from a
uniform distribution between 0.1 and 0.9. TODO CONSIDER BETTER RANGE
HERE

@@

We evaluated two sets of conservation rules of thumb: (1) spatial
response diversity rules of thumb in an idealistic scenario where you
can detect response diversity, and (2) a more realistic scenario where
we know little about response diversity and we're left with a choice of
how many populations to conserve. We then considered how optimal these
strategies were across all possible conservation-prioritization
strategies.

@@

We evaluated four spatial conservation rules of thumb (Figure
\ref{f:curves}). In all spatial scenarios, we conserved four populations
and set the unfished equilibrium biomass of the remaining populations to
near elimination (five salmon). These reduced populations could
therefore still receive straying salmon but were unlikely to re-build on
their own to a substantial abundance. The four scenarios were:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Conserve an even sampling of response diversity. In other words,
  conserve alternating subpopulations.
\item
  Conserve the most stable populations only.
\item
  Conserve one half of the metapopulation.
\item
  Conserve the other half of the metapopulation.
\end{enumerate}

@@

In reality we rarely know precise levels of response diversity. We
therefore additionally considered a case where the conservation was
randomly assigned with respect to response diversity but where different
numbers of streams can be conserved. We considered conserving from two
to 16 streams. Similarly to the spatial strategies, we reduced the
carrying capacity of the remaining streams to the nominal level of five
salmon.

\subsubsection{How optimal are the conservation strategies?}

To test how optimal the strategies were, we generated metapopulation
portfolios in which the investment weights (Ricker $b$ parameters) were
randomly assigned such that the total available ``investment'' remained
constant. This Monte-Carlo strategy illustrates a large sample of
possible portfolios in risk-return space. We then placed the
conservation strategies listed above into this space to determine how
close to the efficient frontier they lie. {[}Figure not shown yet{]}

@@

Figure \ref{f:curves} Figure \ref{f:sp-mv} Figure \ref{f:n-mv}

@@

\begin{table}[h!]
\centering
\small
\caption{Components of salmon metapopulation portfolios}
\begin{tabular}{p{3.6cm}p{7.5cm}}
\toprule
Component          & Definition for the salmon portfolio\\
\midrule
Assets             & Stream-level salmon populations; possibly a Viable Salmonid Population\\
Portfolio          & The salmon metapopulation; possibly an Evolutionarily Significant Unit\\
Portfolio managers & Salmon managers\\
Investors          & Salmon managers, conservation agency, or salmon fishers\\
Asset weights      & Carrying capacity (specifically the $b$ parameters in a Ricker model)\\
Asset returns      & Rate of change of generation-to-generation salmon metapopulation abundance\\
Asset risk         & Variance of generation-to-generation salmon metapopulation abundance\\
\bottomrule
\end{tabular}
\label{t:port}
\end{table}

@@

\begin{table}[h!]
\centering
\small
\caption{Salmon metapopulation parameters with base case and alternate values.}
\begin{tabular}{p{7.0cm}p{1.6cm}p{3.2cm}}
\toprule
Description                                                      & Parameter             & Base [lower, upper] \\
\midrule
Stock-recruit residual standard deviation (on log scale)         & $\sigma_v$            & 0.30 [0.05, 0.50] \\
First order AR(1) serial correlation of stock-recruit residuals  & $\rho_w$              & 0.40 [0, 0.80] \\
Fraction of fish that stray from natal streams                   & $f_{\mathrm{stray}}$  & 0.02 [0, 0.10] \\
Exponential rate of decay of straying with distance              & $m$                   & 0.3 [0.05, 0.5] \\
Standard deviation of beta distribution for implementation error & $\sigma_{h}$          & 0.05 [0, 0.20] \\
Frequency of assessment (years)                                  & $f_{\mathrm{assess}}$ & 5 [1, 20] \\
Environmental tolerance parameters ... & & \\
\bottomrule
\end{tabular}
\label{t:pars}
\end{table}

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=3.0in]{../examples/thermal-curve-scenarios.pdf}
\caption{Different ways of prioritizing response-diversity conservation. Panel (a) shows the thermal tolerance cures for ten possible populations and panels (b--e) show different ways of prioritizing four of those populations. The curves describe how productivity varies with the environment for a given population. Some populations thrive at low environmental values (cool colours) and some at high (warm colours) values. Some are tolerant to a wider range of environmental conditions (yellow-to-green colours) but with a lower maximum productivity. The total possible productivity across environmental values (the area under the curves) is the same.}
\label{f:curves}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=5.0in]{../examples/cons-plans-n.pdf}
\caption{The importance of preserving as many salmon populations as possible when we don't know how response diversity is distributed. In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations (see Fig.~X). We show metapopulations in which 2 (red), 4 (orange), 8 (yellow), or 16 (green) populations of random response diversity are conserved. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation (c) rate-of-change and (d) abundance time series for the short-term environmental-fluctuation scenario.}
\label{f:n-mv}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=5.0in]{../examples/quasi-extinct.pdf}
\caption{First draft of a quasi-extinction figure I THINK THIS WILL BE 
SCRAPPED OR CHANGED. The y-axis shows the cumulative proportion of 
subpopulations that have had abundance dip below a threshold of 20\% 
of unfished equilibrium abundance. We could show a (binomial) 
measure of uncertainty around these if we want to. Some interesting points: the 
cumulative proportion of ``quasi-extinction'' is higher for both ``one half'' 
scenarios. If it's set up correctly, then this means that there's a benefit to 
the subpopulations to investing in a more ``optimal'' portfolio. The }
\label{f:ext}
\end{figure}

>>>>

\begin{itemize}
\item
  Portfolio optimization reveals\ldots{}
\item
  Portfolio theory reveals conservation strategies that\ldots{}
\item
  Intelligent tinkering with ecological portfolios: patterns of
  environmental response diversity drive salmon conservation priorities
\item
  Keeping every cog and wheel\ldots{}
\end{itemize}

\section{Long and rambling abstract that's a bit old now}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Managing risk is fundamental to the conservation of an endangered
  species.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    risk is usually assessed on a population by population basis
  \item
    for metapopulations, we can consider risk for components or risk for
    the whole
  \end{itemize}
\item
  The management of financial portfolios provides another way of
  considering risk for metapopulations.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    performance of weighted assets
  \item
    efficient frontier concept
  \item
    the parallels with ecological metapopulations
  \end{itemize}
\item
  Pacific salmon are an ideal model to consider under the framework of
  portfolio prioritization because of their metapopulation structure,
  their societal importance and threatened status, and the need to
  prioritize conservation efforts.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    portfolio-like structure

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      documented metapopulation structure
    \item
      predators and fisheries often integrate across stocks
    \end{itemize}
  \item
    Highly threatened; highly valued; face many threats

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      damns
    \item
      roads
    \item
      other habitat degradation
    \item
      logging
    \item
      fishing
    \item
      changing climate
    \end{itemize}
  \item
    There's a need for prioritization

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      because of the highly threatened nature
    \item
      conflicting goals for resource use
    \item
      limited resources
    \item
      Existing prioritization schemes
    \end{itemize}
  \end{itemize}
\item
  Portfolio stabilization through systematic asynchrony in salmon
  population dynamics can be driven by stocks responding uniquely to the
  same environment (`response diversity') or by physical features of the
  environment causing stocks to experience different environmental
  forces (`environmental filter').

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    different responses to the environment: response diversity /
    biocomplexity

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      genetic variation by stock
    \item
      can be driven through historical conditions
    \item
      we focus on this here
    \end{itemize}
  \item
    experiencing different environment: environmental filter concept
    (Moran like)

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      spatially spread out, geographical and hydrological features
      filter the environment to create a variety of forces
    \item
      Typically a combination of both
    \end{itemize}
  \item
    Conversely, forces acting against asynchrony

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      inverse: loss of population diversity
    \item
      inverse: moran
    \item
      but also: dispersal
    \item
      and: trophic interactions with synchronized species
    \end{itemize}
  \end{itemize}
\end{itemize}

Here, we ask how a portfolio approach to management can inform the
conservation of metapopulations in a changing world. We ask two primary
questions: (1) What does portfolio optimization tell us about different
spatial approaches to prioritizing metapopulation conservation assuming
that response diversity is spatially distributed? (2) In a scenario
where we don't know the population-level response diversity, what does
portfolio optimization tell us about the number of populations
conserved? To answer these questions, we develop a salmon metapopulation
simulation in which population-specific productivity is driven by
spatially-distributed environmental tolerance and patterns of short- and
long-term climatic change. We then implement different conservation
``rules of thumb'' that control the population-level carrying
capacities. We evaluate the salmon portfolios along risk and return
axes, similarly to how financial portfolios are assessed. Our findings
illustrate that: (1) conserving response diversity buffers
metapopulation risk given short-term climate forcing and rate of return
given long-term climate forcing, (2) conserving more subpopulations
buffers risk regardless of the climate trend, and (3) considering
metapopulations through the lens of portfolio theory provides a useful
additional dimension through which we can evaluate conservation
strategies.

@@

We developed a salmon metapopulation simulation model that includes a
stock-recruit relationship, demographic stochasticity, straying between
populations, varying responses to the environment, escapement target
setting, and implementation uncertainty. Under two kinds of
environmental regimes we tested different conservation rules of thumb
and evaluated these plans in risk-return space similar to how financial
managers evaluate financial portfolios. See Figure \ref{f:sim-flow} for
an illustration of the overall simulation structure. See Table
\ref{t:pars} for a list of the input parameters to our simulation and
their default values. We provide a package \texttt{metafolio} for the
statistical software \texttt{R} \citep{r2013} as an appendix, to carry
out the simulations and analyses we describe in this paper.

@@

In our ecological portfolios, we defined assets as stream-level
populations and the portfolios as salmon metapopulations (Table
\ref{t:port}). We use the terms \textit{stream} and \textit{populations}
interchangeably to represent the portfolio assets. We defined the
portfolio investors as the stakeholders in the fishery and
metapopulation performance. For example, we could consider fisheries
managers, conservation agencies, or First Nations groups as investors.
We defined asset value as the abundance of returning salmon in each
stream and value of the portfolio as the overall metapopulation
abundance. In this scenario, the equivalent to financial rate of return
is the generation-to-generation rate of change of metapopulation
abundance. We defined the financial asset investment weights as the
capacity of the stream populations --- specifically the unfinished
equilibrium stock size --- since maintaining or restoring habitat
requires money, time, and resources.

@@

The salmon metapopulation dynamics in our simulation were governed by a
spawner-return relationship with stochastic demographic noise and by
straying between populations.

@@

We manipulated the capacity and productivity parameters $b$ and $a$ as
part of the portfolio simulation. The capacity parameters $b_i$ were
controlled by the investment weights in the populations. For example, a
large investment in a stream was represented by a larger unfished
equilibrium stock size $b$ for stream $i$. The productivity parameters
$a_{ti}$ were controlled by the interaction between an environmental
signal and the stream-level population environmental-tolerance curves.

We generated the environmental-tolerance parabolas according to

@@

\noindent where $W_i$ controls the width of the curve for population
$i$, $e_t$ represents the environmental value at generation $t$,
$e_i^{\mathrm{opt}}$ represents the optimal environmental value for
population $i$, and $a_i^{\mathrm{max}}$ represents the maximum possible
$a$ value for population $i$. We set the $W_i$ parameters (Table
\ref{t:pars}) and calculated the $a_i^{\mathrm{max}}$ parameters so that
the area under each curve $A_i$ was equal. See Figure \ref{f:curves}a
for example environmental-tolerance curves.

@@

Our simulation used a simple set of rules to establish escapement
targets and harvest the fish. Every $f_\mathrm{assess}$ years (default
of five years) our simulation fitted a spawner-return function and
target harvest rate $H_{\mathrm{tar}}$ was set based on
\citet{hilborn1992} as

@@

\noindent Further, to establish a range of spawner-return values and to
mimic the start of an open-access fishery, for the first 30 years we
drew the fraction of fish harvested randomly from a uniform distribution
between 0.1 and 0.9. We discarded these initial 30 years as a burn-in
period throughout our analyses.

@@

We evaluated two sets of conservation rules of thumb: (1) spatial
response diversity conservation strategies in an idealistic scenario
where you can detect response diversity, and (2) a more realistic
scenario where we know little about response diversity and we're left
with a choice of how many populations to conserve.

@@

We evaluated four spatial conservation rules of thumb (Figure
\ref{f:curves}b--e). In all spatial scenarios, we conserved four
populations and set the unfished equilibrium biomass of the remaining
populations to near elimination (five salmon). These reduced populations
could still receive straying salmon but were unlikely to rebuild on
their own to a substantial abundance. The four scenarios were:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Conserve an even sampling of response diversity.
\item
  Conserve the most stable populations only.
\item
  Conserve one half of the metapopulation.
\item
  Conserve the other half of the metapopulation.
\end{enumerate}

@@

In reality we rarely know precise levels of response diversity. We
therefore additionally considered a case where the conservation was
randomly assigned with respect to response diversity but where different
numbers of streams could be conserved. We considered conserving from two
to 16 streams. Similarly to the spatial strategies, we reduced the
capacity of the remaining streams to the nominal level of five salmon.

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Spatial conservation

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Short-term environment

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      Response diversity conservation affects risk properties of
      portfolio
    \item
      Nearly the same portfolio whether you invest in the most stable or
      the full range of responses
    \item
      Local demographic extinction may be different
    \item
      You can see this for an example metapopulation time series: c, e:
      generation-to-generation fluctuations dampened by response
      diversity - a ying for every yang
    \end{itemize}
  \item
    Long-term environment

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      Response diversity conservation affects return properties of
      portfolio
    \item
      Depends whether you ``get it right'' in choosing the right
      populations to conserve
    \item
      Notably, those that are most productive at first are no longer so
      later
    \item
      You can see what's happening in the example time series: d, f: You
      get it right or wrong in the long run. Response diversity means
      that when one does poorly another is doing well, longterm rate of
      return is stable
    \end{itemize}
  \end{itemize}
\item
  Number

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Short-term environment

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      More is usually better for risk (give ratios)
    \item
      The unknown response diversity causes a risk spread
    \item
      Example time series: Fig 4c: Can see the stabilizing effect of
      number on the rate of change
    \item
      Example time series Fig 4d: The way we've set it up, this also
      affects the absolute abundance - a double whammy
    \end{itemize}
  \item
    Long-term environment

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      The unknown response diversity causes a spread in rate of return -
      some cases do well, some do poorly depending on the selection of
      traits
    \item
      More is also usually better in terms of risk
    \item
      More dampens demographic stochasticity
    \item
      More likely to end up with response diversity?
    \end{itemize}
  \end{itemize}
\end{itemize}

Figure \ref{f:sp-mv}

Figure \ref{f:n-mv}

@@

\begin{table}[h!]
\centering
\small
\caption{Components of salmon metapopulation portfolios KEEP THIS?}
\begin{tabular}{p{3.6cm}p{7.5cm}}
\toprule
Component          & Definition for the salmon portfolio\\
\midrule
Assets             & Stream-level salmon populations; possibly a Viable Salmonid Population\\
Portfolio          & The salmon metapopulation; possibly an Evolutionarily Significant Unit\\
Portfolio managers & Salmon managers\\
Investors          & Salmon managers, conservation agency, or salmon fishers\\
Asset weights      & Carrying capacity (specifically the $b$ parameters in a Ricker model)\\
Asset returns      & Rate of change of generation-to-generation salmon metapopulation abundance\\
Asset risk         & Variance of generation-to-generation salmon metapopulation abundance\\
\bottomrule
\end{tabular}
\label{t:port}
\end{table}

@@

\begin{table}[h!]
\centering
\footnotesize
\caption{Input parameters to the salmon metapopulation simulation with default values.}
\begin{tabular}{p{7.7cm}p{1.4cm}p{3.6cm}}
\toprule
Description                                                                                & Symbol                & Value \\
\midrule

\textit{Population dynamics parameters}                                                             &                       & \\
Stock-recruit residual standard deviation (on log scale)                                   & $\sigma_v$            & 0.30  \\
AR(1) serial correlation of stock-recruit residuals                                        & $\rho_w$              & 0.40  \\
Fraction of fish that stray from natal streams                                             & $f_{\mathrm{stray}}$  & 0.02  \\
Exponential rate of decay of straying with distance                                        & $m$                   & 0.3  \\

\noalign{\vskip 3mm} 
\textit{Environmental parameters}                                                                   &                       & \\
Width of environmental-tolerance curves for populations $i$ 1 to $n$                       & $W_i$                 & seq(0.05, 0.02, 0.02 0.05, length = n pop)\\
Optimum environmental value for populations $i$ 1 to $n$                                   & $e_i^{\mathrm{opt}}$  & seq(13, 19, length = n pop)\\
Area under each environmental-tolerance curve in environmental units                       & $A$                   & 30\\
AR(1) autocorrelation of the environmental signal for the short-term fluctuation scenarios & $\rho_e$              & 0.1 \\
Standard deviation of environmental noise for the short-term fluctuation scenarios         & $\sigma_d$            & 2 \\

\noalign{\vskip 3mm} 
\textit{Fishery parameters}                                                                         &                       & \\
Standard deviation of beta distribution for implementation error                           & $\sigma_{h}$          & 0.05  \\
Frequency of assessment (years)                                                            & $f_{\mathrm{assess}}$ & 5  \\
\bottomrule
\end{tabular}
\label{t:pars}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=3.0in]{../examples/thermal-curve-scenarios.pdf}
\caption{Different ways of prioritizing response-diversity conservation. Panel a shows the thermal tolerance cures for ten possible populations and panels b--e show different ways of prioritizing four of those populations. The curves describe how productivity varies with the environment for a given population. Some populations thrive at low environmental values (cool colours) and some at high (warm colours) values. Some are tolerant to a wider range of environmental conditions (yellow-to-green colours) but with a lower maximum productivity. The total possible productivity (the area under the curves) is the same for each population.}
\label{f:curves}
\end{figure}

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=5.0in]{../examples/cons-plans-n.pdf}
\caption{The importance of preserving as many subpopulations as possible when we don't know how response diversity is distributed. In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations (see Fig.~X). We show metapopulations in which 2 (red), 4 (orange), 8 (yellow), or 16 (green) populations of random response diversity are conserved. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation (c) rate-of-change and (d) abundance time series for the short-term environmental-fluctuation scenario.}
\label{f:n-mv}
\end{figure}

@@

### 2013-06-06 inst/ms/som.tex
A variety of ms updates; split into multiple files
Make a variety of ms edits
A variety of ms updates; especially adding outlines

\begin{figure}[htbp]
\centering
\includegraphics[width=4.0in]{../examples/figure/plot-various-options-ts-3pops.pdf}
\caption{The impact of increasing or decreasing various parameter values in the simulations. The different lines represent different salmon populations.}
\label{f:eg-sens}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=4.0in]{../examples/figure/stray-matrix.pdf}
\caption{ An example straying matrix. The rows and columns represent different populations (indicated by population number). Dark blue indicates a high rate of straying and light blue indicates a low rate of straying.  The straying matrix is generated through equation \ref{eq:stray}.}
\label{f:stray}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=4.5in]{../examples/thermal-curves.pdf}
\caption{The full range of environmental tolerance curves shown for 10 populations. The vertical dotted lines indicate the general range of environmental fluctuations in the main simulations, and the vertical dashed line indicates the mean environmental value in the main simulations.}
\label{f:all-curves}
\end{figure}

@@

A placeholder: \citep{Schindler2010}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=4.0in]{../examples/figure/plot-various-options-ts-3pops.pdf}
\caption{The impact of increasing or decreasing various parameter values in the simulations. The different lines represent different salmon populations. (NEED TO ADD PARAMETER VALUES AND EXPAND THIS SLIGHTLY)}
\label{f:eg-sens}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=4.0in]{../examples/figure/stray-matrix.pdf}
\caption{An example straying matrix. The rows and columns represent different 
populations (indicated by population number). Dark blue indicates a high rate 
of straying and light blue indicates a low rate of straying. The straying 
matrix is generated through equation \ref{eq:stray}.}
\label{f:stray}
\end{figure}

@@

A placeholder: \citep{schindler2010}
